---
title: "p8105_yh3555_hw3"
author: "Yuchen Hua"
date: "2022-10-14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)
library(patchwork)
library(dplyr)
library(readxl)
library(p8105.datasets)
```

## Problem 1
### Read in the data

```{r}
data("instacart")

instacart = 
  instacart %>% 
  as_tibble(instacart)
```


```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

Next is a plot that shows the number of items ordered in each aisle. Here, aisles are ordered by ascending number of items.

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  labs(title = "Number of items ordered in each aisle") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```

Our next table shows the three most popular items in aisles `baking ingredients`, `dog food care`, and `packaged vegetables fruits`, and includes the number of times each item is ordered in your table.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(desc(n)) %>%
  knitr::kable()
```

Finally is a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week. This table has been formatted in an untidy manner for human readers. Pink Lady Apples are generally purchased slightly earlier in the day than Coffee Ice Cream, with the exception of day 5.

```{r}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  spread(key = order_dow, value = mean_hour) %>%
  knitr::kable(digits = 2)
```




## Problem 2
#### Import data and clean dataset
```{r}
accel = read_csv("./data/accel_data.csv")
accel
```

```{r}
accel = read_csv("./data/accel_data.csv")%>%
   janitor::clean_names()%>%
  pivot_longer(activity_1 : activity_1440,
               names_to = "minutes_from_midnight",
               names_prefix = "activity.",
               values_to = "activity") %>%
  mutate(minutes_from_midnight = as.numeric(minutes_from_midnight)) %>%
  mutate(weekend_vs_weekdays = ifelse(day == c("Sunday", "Saturday"), "weekend", "weekday"))
accel
```
 

```{r}
accel = read_csv("./data/accel_data.csv")%>%
   janitor::clean_names()%>%
  pivot_longer(activity_1 : activity_1440,
               names_to = "minutes_from_midnight",
               names_prefix = "activity.",
               values_to = "activity") %>%
  mutate(minutes_from_midnight = as.numeric(minutes_from_midnight)) %>%
  group_by(week, day)%>%
  summarize(total = sum(activity))%>%
  group_by(week, day, total)
accel
```

```{r}
accel = read_csv("./data/accel_data.csv")%>%
  janitor::clean_names()%>%
  pivot_longer(activity_1 : activity_1440,
               names_to = "minutes_from_midnight",
               names_prefix = "activity.",
               values_to = "activity") %>%
  mutate(minutes_from_midnight = as.numeric(minutes_from_midnight))
accel %>%
  ggplot(aes(x = minutes_from_midnight, y = activity, color= day)) + geom_smooth(se= FALSE)  + labs(x = "minutes from midnight", y="activity", title="Activity accounts every day by minutes")
```


## Problem 3
#### Import dataset
```{r}
library(p8105.datasets)
data("ny_noaa")
ny_noaa = ny_noaa %>% as_tibble(ny_noaa)
ny_noaa
```
There are 2595176 columns in the dataset.

#### Clean the data
```{r}
noaa_tidy= ny_noaa %>% 
  separate(col= date, into =  c('year', 'month', 'day')) %>%
  mutate(prcp = prcp/10, tmax = as.numeric(tmax)/10, tmin= as.numeric(tmin)/10)
noaa_tidy
```

#### Figure 1
```{r}
noaa_tidy %>%
  group_by(id, year, month)%>%
  filter(month == c("01", "07"))%>%
  summarise(tmax_mean = mean(tmax, na.rm = TRUE)) %>%
  ggplot(aes(x= year, y = tmax_mean)) + geom_point(alpha = 0.5)+ facet_grid(.~month) + labs(x= "Year", y= "Mean month", title="Average max temperature in January and in July")
```

#### Figure 2
```{r}

```






